### 2024-11-11 Article/Graph_sections/Eq_Graphs_integration.tex
eqgrph pushouts reg mono van kampen

\begin{example}
	TODO: Q does not preserves limits.
\end{example}

@@

\begin{lemma}\label{lemma:reg_push_stable}
	In $\EqGrph$, pushouts along regular monos are stable.
\end{lemma}

@@

>>>>

\begin{example}
	TODO: Q does not preserve limits.
\end{example}

@@

\begin{lemma}\label{lemma:stab}
	In $\EqGrph$, pushouts along regular monos are stable.
\end{lemma}

@@

\begin{lemma}\label{lemma:van_kampen}
	In $\EqGrph$, pushouts along regular monos are $\Reg(\EqGrph)$-Van Kampen.
\end{lemma}

\begin{proof}
	In lieu of \Cref{lem:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
        \[\begin{tikzcd}[row sep=23, column sep =23]
        & {\mathcal{G}_1'} && {\mathcal{G}_2'} \\
        {\mathcal{G}_3'} && {\mathcal{G}_4'} \\
        & {\mathcal{G}_1} && {\mathcal{G}_2} \\
        {\mathcal{G}_3} && {\mathcal{G}_4}
        \arrow["{h'}", from=1-2, to=1-4]
        \arrow["{k'}"', from=1-2, to=2-1]
        \arrow["b"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'}", from=1-4, to=2-3]
        \arrow["c", from=1-4, to=3-4]
        \arrow["{p'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["a"', from=2-1, to=4-1]
        \arrow["h"{pos=0.7}, from=3-2, to=3-4]
        \arrow["d"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["k"', from=3-2, to=4-1]
        \arrow["t", from=3-4, to=4-3]
        \arrow["p"', from=4-1, to=4-3]
        \end{tikzcd}\]
        By \Cref{prop:eqgrph_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces, thus their front faces are pullbacks too.
        \[\begin{tikzcd}[row sep=20, column sep = 20]
        & {A_1'} && {A_2'} \\
        {A_3'} && {A_4'} \\
        & {A_1} && {A_2} \\
        {A_3} && {A_4}
        \arrow["{h'_V}", from=1-2, to=1-4]
        \arrow["{k'_V}"', from=1-2, to=2-1]
        \arrow["{b_V}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_V}", from=1-4, to=2-3]
        \arrow["{c_V}", from=1-4, to=3-4]
        \arrow["{p'_V}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_V}"', from=2-1, to=4-1]
        \arrow["{h_V}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_V}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_V}"', from=3-2, to=4-1]
        \arrow["{t_V}", from=3-4, to=4-3]
        \arrow["{p_V}"', from=4-1, to=4-3]
        \end{tikzcd}\qquad
        \begin{tikzcd}[row sep=20, column sep = 20]
        & {B_1'} && {B_2'} \\
        {B_3'} && {B_4'} \\
        & {B_1} && {B_2} \\
        {B_3} && {B_4}
        \arrow["{h'_E}", from=1-2, to=1-4]
        \arrow["{k'_E}"', from=1-2, to=2-1]
        \arrow["{b_E}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow["{t'_E}", from=1-4, to=2-3]
        \arrow["{c_E}"', from=1-4, to=3-4]
        \arrow["{p'_E}"{pos=0.8}, from=2-1, to=2-3, crossing over]
        \arrow["{a_E}"', from=2-1, to=4-1]
        \arrow["{h_E}"{pos=0.7}, from=3-2, to=3-4]
        \arrow["{d_E}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
        \arrow["{k_E}"', from=3-2, to=4-1]
        \arrow["{t_E}", from=3-4, to=4-3]
        \arrow["{p_E}"', from=4-1, to=4-3]
        \end{tikzcd}
        \]

	On the other hand we can consider the diagrams below, in which the inner squares are pullbacks. Since the outer diagrams commute, by definition of porphism of $\EqGrph$, then we have the existence of $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.

	\[\begin{tikzcd}[row sep = 20, column sep = 20]
	{C'_3} &&& {C_2'} \\
	& Y & {C'_4} & {} & U & {C_4'} \\
	& {C_3} & {C_4} && {C_2} & {C_4}
	\arrow["{m_3}", dashed, from=1-1, to=2-2]
	\arrow["{p'_C}", from=1-1, to=2-3, bend left = 20]
	\arrow["{c_C}"', from=1-1, to=3-2, bend right = 20]
	\arrow["{m_2}", dashed, from=1-4, to=2-5]
	\arrow["{t'_C}", from=1-4, to=2-6, bend left = 20]
	\arrow["{b_C}"', from=1-4, to=3-5, bend right = 20]
	\arrow["{y_1}", from=2-2, to=2-3]
	\arrow["{y_2}"', from=2-2, to=3-2]
	\arrow["{d_C}", from=2-3, to=3-3]
	\arrow["{u_1}", from=2-5, to=2-6]
	\arrow["{u_2}"', from=2-5, to=3-5]
	\arrow["{d_C}", from=2-6, to=3-6]
	\arrow["{p_C}"', from=3-2, to=3-3]
	\arrow["{t_C}"', from=3-5, to=3-6]
	\end{tikzcd}\]
	\[\begin{tikzcd}[row sep = 20, column sep = 20]
	{B_3'} & {B'_4} && {B'_2} & {B'_4} \\
	{C'_3} & Y & {C'_4} & {C_2'} & U & {C_4'} \\
	& {C_3} & {C_4} && {C_2} & {C_4}
	\arrow["{p'_V}", from=1-1, to=1-2]
	\arrow["{q'_3}"', from=1-1, to=2-1]
	\arrow["f", dashed, from=1-1, to=2-2]
	\arrow["{q'_4}", from=1-2, to=2-3]
	\arrow["{t'_V}", from=1-4, to=1-5]
	\arrow["{q'_2}"', from=1-4, to=2-4]
	\arrow["g", dashed, from=1-4, to=2-5]
	\arrow["{q'_4}", from=1-5, to=2-6]
	\arrow["{c_C}"', from=2-1, to=3-2]
	\arrow["{y_1}", from=2-2, to=2-3]
	\arrow["{y_2}"', from=2-2, to=3-2]
	\arrow["{d_C}", from=2-3, to=3-3]
	\arrow["{b_C}"', from=2-4, to=3-5]
	\arrow["{u_1}", from=2-5, to=2-6]
	\arrow["{u_2}"', from=2-5, to=3-5]
	\arrow["{d_C}", from=2-6, to=3-6]
	\arrow["{p_C}"', from=3-2, to=3-3]
	\arrow["{t_C}"', from=3-5, to=3-6]
\end{tikzcd}\]

	Now, notice that $m_3$ and $m_2$ are monos because $c_C$ and $b_C$ are monos (\Cref{cor:regmono}). By the proof of \Cref{prop:eqgrph_complete}, to conclude it is enough to show that
	\[\begin{split}
		m_3 \circ q'_3 = f
	\end{split}
	\qquad
	\begin{split}
		m_2\circ q'_2 = g
	\end{split}\]
	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $f$ and $g$, and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:eqgrph_complete}.

	Now, if we compute, we obtain:
	\[\begin{split}
		y_1 \circ f &= q'_4 \circ p'_V \\ &= p'_C \circ q'_3 \\ &= y_1 \circ m_3 \circ q'_3
	\end{split}
	\qquad
	\begin{split}
		u_1 \circ g &= q'_4 \circ t'_V \\ &= t'_C \circ q'_3 \\ &= u_1 \circ m_2 \circ q'_2
	\end{split}\]
	\[\begin{split}
		y_2 \circ f &= d_C \circ q'_3 \\ &= y_2 \circ m_3 \circ q'_3
	\end{split}
	\qquad
	\begin{split}
		u_2 \circ g &= d_V \circ q'_2 \\ &= u_2 \circ m_2 \circ q'_2
	\end{split}\]
	Concluding the proof.
\end{proof}

From \Cref{prop:eqgrph_complete} and \Cref{lemma:stab,lemma:van_kampen}, by \Cref{th:crit_for_adh}, we can deduce at once the following.

\begin{cor}\label{cor:eqgrph_reg_adh}
	$\EqGrph$ is $\Reg(\EqGrph)$-adhesive.
\end{cor}
